---
title: "Data Management"
author: "Teirra"
date: "Friday, February 20, 2015"
output: html_document
---

Subset for H1DA5 that did play a sport    
Can't get H1DA8 and H1DA10 blanks to go into subset

## Purpose of the study
The purpose of this research is to find a correlation between lack of physical activity and an increase in the amount of time adolescent spend watching TV. With the increased time spent in front of the TV more adolescents are becoming obese because they are less physically active.

```{r}
library(PDS)
```
## Variables
These variables are there to show the amount of time adolescent spend watch TV and playing video games, all while being compared to the number of times these adolescents played any type of sport during the week.

```{r}
addhealth.subset <-AddHealth[AddHealth$H1DA5 == 0,]
library(Hmisc)
label(AddHealth$H1DA5) <- "Number of times playing sports this week"
label(AddHealth$H1DA8) <- "Hours spent watching TV"
label(AddHealth$H1DA10) <- "Hours spent playing videogames"
library("descr")

summary(AddHealth$H1DA8)
AddHealth$H1DA8[AddHealth$H1DA8 == 996] <- NA
AddHealth$H1DA8[AddHealth$H1DA8 == 998] <- NA
summary(AddHealth$H1DA8)

freq(as.ordered(AddHealth$H1DA5))
freq(as.ordered(AddHealth$H1DA8))
hist(AddHealth$H1DA8, xlab = "Hours per week", 
     main = "Watching TV", col = "red")
freq(as.ordered(AddHealth$H1DA10))

```
## How data was managed
 This data is organized buy order. The number times adolescents did NOT play any type of sport during the week. Then is shows how many adolescences watch between 0-99 hours of TV during the week. As well as how many hour adolescents spent between 0-99 hours playing video games.
## Histograph
My histogram shows how many hours adolescents spent watching TV. The range goes from 0-99 and peaks between 0-10 hours.
 