---
title: "Moderation Assignment"
date: "Tuesday, April 14, 2015"
output: html_document
---

```{r}
knitr::opts_chunk$set(comment = NA, message = FALSE, warning = FALSE, fig.align = "center")
```
##################################################################
### Purpose of the study
##################################################################
Concern over the rapid increase in childhood obesity in the US has been widely expressed in the medical literature. Over the past couple of decades, the obesity rate has been on a steady increase. Also with that increase there has also been an increase in amount of time society spends watching TV. Less physically active children and those who watched more television after school were more likely to become overweight. The correlation between BMI (body mass index) and how it has an effect on individuals that spend in increase amount of time watching TV, will also show a correlation between people that are physically active in their daily life.The purpose of this research is to find a correlation between lack of physical activity and an increase in the amount of time adolescent spend watching TV. With the increased time spent in front of the TV more adolescents are becoming obese because they are less physically active.


################################################################
## Variables
################################################################
These variables are there to show `Hours spent watching TV` and `Hours spent playing videogames` by adolescents, all while being compared to `Number of times playing sports this week` by those same adolescents.


#################################################################
## How data was managed
#################################################################
 This data is organized by order. The number times adolescents did NOT play any type of sport during the week. Then is shows how many adolescences watch between 0-99 hours of TV during the week. As well as how many hour adolescents spent between 0-99 hours playing video games.
 
 
###############################################################
```{r echo=FALSE}
library(PDS)
library(descr)
library(Hmisc)
library(dplyr)
library(ggplot2)
```
###############################################################


###############################################################
## Data Management
###############################################################
```{r}
AHS <- AddHealth %>%
  filter(H1DA5!=0) %>%
  select(H1DA5,H1DA8,H1DA10)
head(AHS)

AHS <- AHS %>%
  rename(Sports=H1DA5, TV=H1DA8, VideoGames=H1DA10)
head(AHS)


label(AHS$Sports) <- "Number of times playing sports this week"
label(AHS$TV) <- "Hours spent watching TV"
label(AHS$VideoGames) <- "Hours spent playing videogames"


AHS$Sports[AHS$Sports == 6] <- NA
AHS$Sports[AHS$Sports == 8] <- NA
summary(AHS)
AHS$Sports <- factor(AHS$Sports)[,drop=TRUE]
summary(AHS$Sports)

AHS$TV[AHS$TV == 996] <- NA
AHS$TV[AHS$TV == 998] <- NA
summary(AHS$TV)

AHS$VideoGames[AHS$VideoGames == 996] <- NA
AHS$VideoGames[AHS$VideoGames == 998] <- NA
summary(AHS$VideoGames)


#making the two quantitative vaiables into categorical for chi-square test.
AHS$GroupieTV <- as.factor(cut(AHS$TV, breaks=c(0,5,12,21,100),include.lowest=TRUE, labels=c("0-5 hours", "5-12 hours", "12-21 hours", "21-100 hours")))
summary(AHS$GroupieTV)

AHS$GroupieVG <- as.factor(cut(AHS$VideoGames, breaks=c(0,1,3,100),include.lowest=TRUE, labels=c("0-1 hours", "1-3 hours", "more than 3 hours")))
summary(AHS$GroupieVG)
head(AHS)

```

#Catergorical Variable:
This graph is a representation of how many times per week the adolescents from this study participate in playing any type of active sport. The majority either play `1 or 2 times` or `5 or more times` during the week.

```{r}
AHS$Sports <- factor(AHS$Sports,
                    labels = c("1 or 2 times", "3 or 4 times", "5 or more times"))

freq((AHS$Sports), main = "Adolescents playing sports", ylab = "Frequency", xlab = "Number of times per week", col = "red")
```

#Quantitative Variable:
This frequency graph is skewed left and shows how often adolescents from the previous study spend `Watching TV`. Most of them watch less the `13 hours` but there is a spike at `10 hours`.

```{r}
summary(AHS$TV)
freq((AHS$TV), main = "Adolescents Watching TV", ylab = "Frequency", xlab = "Number of hours per week", col = "blue")
```

#Quantitative Variable:
This density graph show how many hours adolescents spend playing video games during a given week. This graph is skewed left and peaks at around 1-2 hours. There is a drastic decrease around 5 hours and then it continues to fluctuate after 10 hours.

```{r}
summary(AHS$VideoGames)
plot(density(AHS$VideoGames, na.rm=TRUE),col="Orange", main="Adolescents Playing Video Games", xlab="Number of hours per week")
```

###############################################################
##MultiVariant Graph
###############################################################
```{r}
table(AHS$GroupieTV,AHS$Sports)
prop.table(table(AHS$GroupieTV,AHS$Sports))
barplot(prop.table(table(AHS$GroupieTV,AHS$Sports)), main="Relationship between Adolescents that play sports and watch tv", xlab= "Hours per week watching TV", ylab= "# of times playing a sport")
```

This multivariate graph shoes a comparison between the number of times adolescents play an active sport during a given week and hour many hours the spend watch TV.

###############################################################
### ANOVA
###############################################################

#Null Hypothesis
```{r echo=FALSE}
mod <- aov(TV~Sports, data=AHS)
summary(mod)
```

With this to summary, it is shown that there is to large of a difference to determine if these variable have a relation. It does not mean that the hypothesis is not true, it is simply saying that it can not be determined that it is false.

#Rejected Hypothesis
```{r echo=FALSE}
mad <- aov(VideoGames~Sports, data=AHS)
summary(mad)
```

With this, it has been determined that there is at least one great significance in this data frame, because our p value is 4.04e-05.While this does not specify what set has the significant difference, it does tell us that there is one and that is what we need to look for. This is where the Post Hoc test comes into play.

##Post HOC Test
```{r echo=FALSE}
tapply(AHS$VideoGames, AHS$Sports, mean, na.rm=TRUE)
tapply(AHS$VideoGames, AHS$Sports, sd, na.rm=TRUE)
tapply(AHS$VideoGames, AHS$Sports, median, na.rm=TRUE)

ggplot(data=AHS,aes(x=Sports,y=VideoGames))+
  geom_boxplot(colour = "Red")
```

This table shows the comparison between Adolescents the play sports during a given week, and those same adolescents number of hours playing video games. The mean number of people the play an active sport `5 or more times` during a given week has a significant difference than those that play an active sport `1 or 2 times` a week.

```{r}
TukeyHSD(mad)
```

####################################################################
##Chi-Sq Test
####################################################################
```{r}
T1 <-xtabs(~Sports+GroupieTV, data=AHS)
chisq.test(T1)
T2 <-xtabs(~Sports+GroupieVG, data=AHS)
chisq.test(T2)
T3 <-xtabs(~GroupieTV+GroupieVG, data=AHS)
chisq.test(T3)

ggplot(data = na.omit(AHS), aes(x = GroupieTV, fill = GroupieVG)) + 
  geom_bar(position = "fill") + 
  theme_bw()
```

With my Chi square test, it is shown that the p value is greater than our alpha value(0.05) for T1, T2, this shows that these two variables are independent. As for our T3 Chi square test our p value is less than alpha value(0.05) with a value of 2.2e-16. This means that `GroupieVG` and `GroupieTV` are dependent variables.

############################################################
#Post HOC Test
############################################################
```{r}
chisq.test(T3[, c(1, 2)]) # significant
chisq.test(T3[, c(1, 3)]) # significant
chisq.test(T3[, c(2, 3)]) # significant
  
library(vcd)
mosaic(T3, shade = TRUE)
```

This final graph shows that there is an association between the `GroupieTV` variable and `GroupieVG` variable. This tells us there there is an association with the amount of time adolescent spend watching TV and the amount of time the spend playing video games. When the amount of time the spend watching TV increase, the amount of time they spend playing video games also increase, showing that these to variable to be dependent.

############################################################
##Corrrelation
############################################################

```{r}
library(PDS)
head(AHS)
#plot(VideoGames ~ TV, data=AHS)
mud <- lm(VideoGames ~ TV, data=AHS)
summary(mud)
#abline(mud)
cor(AHS$VideoGames, AHS$TV)
cor.test(AHS$VideoGames, AHS$TV)

library(ggplot2)
ggplot(data=AHS, aes(x=TV, y=VideoGames))+
  geom_point()+
  theme_bw()+
  geom_smooth(method="lm")
```

This graph shows that there is a weak positive relationship  because our correlation is closer to zero, but there is still a statistic significance between the variables. The P value is very small (2.2e-16) which is less than 5%, but the correlation is only about 32%. Since this correlation is small we can only predict about 10% variability in our variables.
```{r}
#r^2= predicted variability
```

#############################################################
##Moderation
#############################################################

```{r}
tapply(AHS$VideoGames, list(AHS$Sports), mean, na.rm=TRUE)
AHS.aov <- aov(VideoGames ~ Sports, data=AHS)
summary(AHS.aov)
TukeyHSD(AHS.aov)
interaction.plot(AHS$GroupieTV, AHS$Sports, AHS$VideoGames)

library(ggplot2)
p1 <- ggplot(data = AHS, aes(x = GroupieTV, y = VideoGames, colour = Sports, group = Sports, linetype = Sports)) + 
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line") +
  theme_bw() + 
  labs(y = "Hours playing Video Games")
p1
```
The above graph shows that there is an interaction between the number of time adolescent play a sport during a week (`Sports`), the amount of time the spend watching TV during a week (`TV`), and the amount of time they spend playing video games during a week (`VideoGames`).
